# Scales (Guitar)

Plotting the intervals of a scale onto the guitar fretboard allows us to identify patterns for playing the scale at different positions of the neck. These patterns are universal between all keys of the scale and, when combined, they cover all available notes in the key across the fretboard. To use these patterns in different keys you simply shift them up or down the neck. The references below all start on C, so if you wanted to play in D Ionian for example, you should shift each position up two semitones.

## Ionian Mode

**Intervals:** P1 M2 M3 P4 P5 M6 M7

```{r}
### I should find a way to make the plotting code cleaner (maybe a function wrapper for default settings?)

# position 1 ------------------------------------------------------------------

# notes
string_p1 <- c(6, 6,  6, 5, 5,  5, 4, 4,  4, 3, 3,  3, 2,  2, 1, 1,  1)
fret_p1   <- c(7, 8, 10, 7, 8, 10, 7, 9, 10, 7, 9, 10, 8, 10, 7, 8, 10)

# colors
idx_p1 <- c(2, 1, rep(2, 6), 1, rep(2, 6), 1, 2)
pt_fill_p1 <- c("firebrick1", "black")[idx_p1]

# plot
p1 <- tabr::plot_fretboard(string_p1, fret_p1, "notes",
                     fret_range = c(7, 11), show_tuning = TRUE, 
                     point_fill = pt_fill_p1, asp = 1.25, point_size = 8) +
  ggplot2::ggtitle("Position 1")

# position 2 ------------------------------------------------------------------

# notes
string_p2 <- c(6,   6,  6,  5,  5, 4,  4,  4, 3,  3,  3,  2,  2,  2,  1,  1,  1)
fret_p2   <- c(10, 12, 13, 10, 12, 9, 10, 12, 9, 10, 12, 10, 12, 13, 10, 12, 13)

# colors
idx_p2 <- c(rep(2, 6), 1, rep(2, 6), 1, rep(2, 3))
pt_fill_p2 <- c("firebrick1", "black")[idx_p2]

# plot
p2 <- tabr::plot_fretboard(string_p2, fret_p2, "notes",
                     fret_range = c(9, 14), show_tuning = TRUE, 
                     point_fill = pt_fill_p2, asp = 1.25, point_size = 8) +
  ggplot2::ggtitle("Position 2")

# position 3 ------------------------------------------------------------------

# notes
string_p3 <- c(6, 6, 6, 5, 5, 5, 4, 4, 4, 3, 3, 2, 2, 2, 1, 1, 1)
fret_p3   <- c(0, 1, 3, 0, 2, 3, 0, 2, 3, 0, 2, 0, 1, 3, 0, 1, 3)

# colors
idx_p3 <- c(rep(2, 5), 1, rep(2, 6), 1, rep(2, 4))
pt_fill_p3 <- c("firebrick1", "black")[idx_p3]

# plot
p3 <- tabr::plot_fretboard(string_p3, fret_p3, "notes",
                     fret_range = c(0, 4), show_tuning = TRUE, 
                     point_fill = pt_fill_p3, asp = 1.25, point_size = 8) +
  ggplot2::ggtitle("Position 3")

# position 4 ------------------------------------------------------------------

# notes
string_p4 <- c(6, 6, 5, 5, 5, 4, 4, 4, 3, 3, 3, 2, 2, 2, 1, 1)
fret_p4   <- c(3, 5, 2, 3, 5, 2, 3, 5, 2, 4, 5, 3, 5, 6, 3, 5)

# colors
idx_p4 <- c(rep(2, 3), 1, rep(2, 6), 1, rep(2, 5))
pt_fill_p4 <- c("firebrick1", "black")[idx_p4]

# plot
p4 <- tabr::plot_fretboard(string_p4, fret_p4, "notes",
                     fret_range = c(2, 7), show_tuning = TRUE, 
                     point_fill = pt_fill_p4, asp = 1.25, point_size = 8) +
  ggplot2::ggtitle("Position 4")

# position 5 ------------------------------------------------------------------

# notes
string_p5 <- c(6, 6, 6, 5, 5, 5, 4, 4, 3, 3, 3, 2, 2, 2, 1, 1, 1)
fret_p5   <- c(5, 7, 8, 5, 7, 8, 5, 7, 4, 5, 7, 5, 6, 8, 5, 7, 8)

# colors
idx_p5 <- c(rep(2, 2), 1, rep(2, 6), 1, rep(2, 6), 1)
pt_fill_p5 <- c("firebrick1", "black")[idx_p5]

# plot
p5 <- tabr::plot_fretboard(string_p5, fret_p5, "notes",
                     fret_range = c(4, 9), show_tuning = TRUE, 
                     point_fill = pt_fill_p5, asp = 1.25, point_size = 8) +
  ggplot2::ggtitle("Position 5")

# all positions ---------------------------------------------------------------

pA <- tabr::plot_fretboard(
  c(string_p1, string_p2, string_p3, string_p4, string_p5),
  c(fret_p1, fret_p2, fret_p3, fret_p4, fret_p5),
  "notes", horizontal = TRUE, fret_range = c(0, 14), show_tuning = TRUE,
  asp = 0.25, point_size = 8,
  point_fill = c(pt_fill_p1, pt_fill_p2, pt_fill_p3, pt_fill_p4, pt_fill_p5)
  ) +
  ggplot2::ggtitle("All Positions")

```
```{r, fig.height=2.5}
# patchwork
library(patchwork)
pA
```

```{r, fig.height=6.5}
p1 + p2 + p3 + p4 + p5 + 
  plot_layout(ncol = 3)
```

## Dorian Mode

**Intervals:** P1 M2 m3 P4 P5 M6 m7

```{r}

# position 1 ------------------------------------------------------------------

# notes
string_p1 <- c(6,   6,  6,  5,  5, 4,  4,  4, 3,  3,  3,  2,  2,  2,  1,  1,  1)
fret_p1   <- c(10, 12, 13, 10, 12, 9, 10, 12, 9, 10, 12, 10, 12, 13, 10, 12, 13)

# colors
idx_p1 <- c(1, rep(2, 6), 1, rep(2, 6), 1, rep(2, 2))
pt_fill_p1 <- c("firebrick1", "black")[idx_p1]

# plot
p1 <- tabr::plot_fretboard(string_p1, fret_p1, "notes",
                     fret_range = c(9, 14), show_tuning = TRUE, 
                     point_fill = pt_fill_p1, asp = 1.25, point_size = 8) +
  ggplot2::ggtitle("Position 1")

# position 2 ------------------------------------------------------------------

# notes
string_p2 <- c(6, 6, 6, 5, 5, 5, 4, 4, 4, 3, 3, 2, 2, 2, 1, 1, 1)
fret_p2   <- c(0, 1, 3, 0, 2, 3, 0, 2, 3, 0, 2, 0, 1, 3, 0, 1, 3)

# colors
idx_p2 <- c(rep(2, 6), 1, rep(2, 6), 1, rep(2, 3))
pt_fill_p2 <- c("firebrick1", "black")[idx_p2]

# plot
p2 <- tabr::plot_fretboard(string_p2, fret_p2, "notes",
                     fret_range = c(0, 4), show_tuning = TRUE, 
                     point_fill = pt_fill_p2, asp = 1.25, point_size = 8) +
  ggplot2::ggtitle("Position 2")

# position 3 ------------------------------------------------------------------

# notes
string_p3 <- c(6, 6, 5, 5, 5, 4, 4, 4, 3, 3, 3, 2, 2, 2, 1, 1)
fret_p3   <- c(3, 5, 2, 3, 5, 2, 3, 5, 2, 4, 5, 3, 5, 6, 3, 5)

# colors
idx_p3 <- c(rep(2, 4), 1, rep(2, 6), 1, rep(2, 4))
pt_fill_p3 <- c("firebrick1", "black")[idx_p3]

# plot
p3 <- tabr::plot_fretboard(string_p3, fret_p3, "notes",
                     fret_range = c(2, 7), show_tuning = TRUE, 
                     point_fill = pt_fill_p3, asp = 1.25, point_size = 8) +
  ggplot2::ggtitle("Position 3")

# position 4 ------------------------------------------------------------------

# notes
string_p4 <- c(6, 6, 6, 5, 5, 5, 4, 4, 3, 3, 3, 2, 2, 2, 1, 1, 1)
fret_p4   <- c(5, 7, 8, 5, 7, 8, 5, 7, 4, 5, 7, 5, 6, 8, 5, 7, 8)

# colors
idx_p4 <- c(rep(2, 3), 1, rep(2, 6), 1, rep(2, 6))
pt_fill_p4 <- c("firebrick1", "black")[idx_p4]

# plot
p4 <- tabr::plot_fretboard(string_p4, fret_p4, "notes",
                     fret_range = c(4, 9), show_tuning = TRUE, 
                     point_fill = pt_fill_p4, asp = 1.25, point_size = 8) +
  ggplot2::ggtitle("Position 4")

# position 5 ------------------------------------------------------------------

# notes
string_p5 <- c(6, 6,  6, 5, 5,  5, 4, 4,  4, 3, 3,  3, 2,  2, 1, 1,  1)
fret_p5   <- c(7, 8, 10, 7, 8, 10, 7, 9, 10, 7, 9, 10, 8, 10, 7, 8, 10)

# colors
idx_p5 <- c(rep(2, 2), 1, rep(2, 6), 1, rep(2, 6), 1)
pt_fill_p5 <- c("firebrick1", "black")[idx_p5]

# plot
p5 <- tabr::plot_fretboard(string_p5, fret_p5, "notes",
                     fret_range = c(7, 11), show_tuning = TRUE, 
                     point_fill = pt_fill_p5, asp = 1.25, point_size = 8) +
  ggplot2::ggtitle("Position 5")

# all positions ---------------------------------------------------------------

pA <- tabr::plot_fretboard(
  c(string_p1, string_p2, string_p3, string_p4, string_p5),
  c(fret_p1, fret_p2, fret_p3, fret_p4, fret_p5),
  "notes", horizontal = TRUE, fret_range = c(0, 14), show_tuning = TRUE,
  asp = 0.25, point_size = 8,
  point_fill = c(pt_fill_p1, pt_fill_p2, pt_fill_p3, pt_fill_p4, pt_fill_p5)
  ) +
  ggplot2::ggtitle("All Positions")

```

```{r, fig.height=2.5}
pA
```

```{r, fig.height=6.5}
p1 + p2 + p3 + p4 + p5 + 
  plot_layout(ncol = 3)
```

## Phrygian Mode

**Intervals:** P1 m2 m3 P4 P5 m6 m7

```{r}
# position 1 ------------------------------------------------------------------

# notes
string_p1 <- c(6, 6, 6, 5, 5, 5, 4, 4, 4, 3, 3, 2, 2, 2, 1, 1, 1)
fret_p1   <- c(0, 1, 3, 0, 2, 3, 0, 2, 3, 0, 2, 0, 1, 3, 0, 1, 3)

# colors
idx_p1 <- c(1, rep(2, 6), 1, rep(2, 6), 1, rep(2, 2))
pt_fill_p1 <- c("firebrick1", "black")[idx_p1]

# plot
p1 <- tabr::plot_fretboard(string_p1, fret_p1, "notes",
                     fret_range = c(0, 4), show_tuning = TRUE, 
                     point_fill = pt_fill_p1, asp = 1.25, point_size = 8) +
  ggplot2::ggtitle("Position 1")

# position 2 ------------------------------------------------------------------

# notes
string_p2 <- c(6, 6, 5, 5, 5, 4, 4, 4, 3, 3, 3, 2, 2, 2, 1, 1)
fret_p2   <- c(3, 5, 2, 3, 5, 2, 3, 5, 2, 4, 5, 3, 5, 6, 3, 5)

# colors
idx_p2 <- c(rep(2, 5), 1, rep(2, 6), 1, rep(2, 3))
pt_fill_p2 <- c("firebrick1", "black")[idx_p2]

# plot
p2 <- tabr::plot_fretboard(string_p2, fret_p2, "notes",
                     fret_range = c(2, 7), show_tuning = TRUE, 
                     point_fill = pt_fill_p2, asp = 1.25, point_size = 8) +
  ggplot2::ggtitle("Position 2")

# position 3 ------------------------------------------------------------------

# notes
string_p3 <- c(6, 6, 6, 5, 5, 5, 4, 4, 3, 3, 3, 2, 2, 2, 1, 1, 1)
fret_p3   <- c(5, 7, 8, 5, 7, 8, 5, 7, 4, 5, 7, 5, 6, 8, 5, 7, 8)

# colors
idx_p3 <- c(rep(2, 4), 1, rep(2, 6), 1, rep(2, 5))
pt_fill_p3 <- c("firebrick1", "black")[idx_p3]

# plot
p3 <- tabr::plot_fretboard(string_p3, fret_p3, "notes",
                     fret_range = c(4, 9), show_tuning = TRUE, 
                     point_fill = pt_fill_p3, asp = 1.25, point_size = 8) +
  ggplot2::ggtitle("Position 3")

# position 4 ------------------------------------------------------------------

# notes
string_p4 <- c(6, 6,  6, 5, 5,  5, 4, 4,  4, 3, 3,  3, 2,  2, 1, 1,  1)
fret_p4   <- c(7, 8, 10, 7, 8, 10, 7, 9, 10, 7, 9, 10, 8, 10, 7, 8, 10)

# colors
idx_p4 <- c(rep(2, 3), 1, rep(2, 6), 1, rep(2, 6))
pt_fill_p4 <- c("firebrick1", "black")[idx_p4]

# plot
p4 <- tabr::plot_fretboard(string_p4, fret_p4, "notes",
                     fret_range = c(7, 11), show_tuning = TRUE, 
                     point_fill = pt_fill_p4, asp = 1.25, point_size = 8) +
  ggplot2::ggtitle("Position 4")

# position 5 ------------------------------------------------------------------

# notes
string_p5 <- c(6,   6,  6,  5,  5, 4,  4,  4, 3,  3,  3,  2,  2,  2,  1,  1,  1)
fret_p5   <- c(10, 12, 13, 10, 12, 9, 10, 12, 9, 10, 12, 10, 12, 13, 10, 12, 13)

# colors
idx_p5 <- c(2, 1, rep(2, 6), 1, rep(2, 6), 1, 2)
pt_fill_p5 <- c("firebrick1", "black")[idx_p5]

# plot
p5 <- tabr::plot_fretboard(string_p5, fret_p5, "notes",
                     fret_range = c(9, 14), show_tuning = TRUE, 
                     point_fill = pt_fill_p5, asp = 1.25, point_size = 8) +
  ggplot2::ggtitle("Position 5")

# all positions ---------------------------------------------------------------

pA <- tabr::plot_fretboard(
  c(string_p1, string_p2, string_p3, string_p4, string_p5),
  c(fret_p1, fret_p2, fret_p3, fret_p4, fret_p5),
  "notes", horizontal = TRUE, fret_range = c(0, 14), show_tuning = TRUE,
  asp = 0.25, point_size = 8,
  point_fill = c(pt_fill_p1, pt_fill_p2, pt_fill_p3, pt_fill_p4, pt_fill_p5)
  ) +
  ggplot2::ggtitle("All Positions")

```

```{r, fig.height=2.5}
pA
```

```{r, fig.height=6.5}
p1 + p2 + p3 + p4 + p5 + 
  plot_layout(ncol = 3)
```

## Lydian

**Intervals:** P1 M2 M3 A4 P5 M6 M7

```{r}
# position 1 ------------------------------------------------------------------

# notes
string_p1 <- c(6, 6, 6, 5, 5, 5, 4, 4, 4, 3, 3, 2, 2, 2, 1, 1, 1)
fret_p1   <- c(0, 1, 3, 0, 2, 3, 0, 2, 3, 0, 2, 0, 1, 3, 0, 1, 3)

# colors
idx_p1 <- c(2, 1, rep(2, 6), 1, rep(2, 6), 1, 2)
pt_fill_p1 <- c("firebrick1", "black")[idx_p1]

# plot
p1 <- tabr::plot_fretboard(string_p1, fret_p1, "notes",
                     fret_range = c(0, 4), show_tuning = TRUE, 
                     point_fill = pt_fill_p1, asp = 1.25, point_size = 8) +
  ggplot2::ggtitle("Position 1")

# position 2 ------------------------------------------------------------------

# notes
string_p2 <- c(6, 6, 5, 5, 5, 4, 4, 4, 3, 3, 3, 2, 2, 2, 1, 1)
fret_p2   <- c(3, 5, 2, 3, 5, 2, 3, 5, 2, 4, 5, 3, 5, 6, 3, 5)

# colors
idx_p2 <- c(rep(2, 6), 1, rep(2, 6), 1, rep(2, 2))
pt_fill_p2 <- c("firebrick1", "black")[idx_p2]

# plot
p2 <- tabr::plot_fretboard(string_p2, fret_p2, "notes",
                     fret_range = c(2, 7), show_tuning = TRUE, 
                     point_fill = pt_fill_p2, asp = 1.25, point_size = 8) +
  ggplot2::ggtitle("Position 2")

# position 3 ------------------------------------------------------------------

# notes
string_p3 <- c(6, 6, 6, 5, 5, 5, 4, 4, 3, 3, 3, 2, 2, 2, 1, 1, 1)
fret_p3   <- c(5, 7, 8, 5, 7, 8, 5, 7, 4, 5, 7, 5, 6, 8, 5, 7, 8)

# colors
idx_p3 <- c(rep(2, 5), 1, rep(2, 6), 1, rep(2, 4))
pt_fill_p3 <- c("firebrick1", "black")[idx_p3]

# plot
p3 <- tabr::plot_fretboard(string_p3, fret_p3, "notes",
                     fret_range = c(4, 9), show_tuning = TRUE, 
                     point_fill = pt_fill_p3, asp = 1.25, point_size = 8) +
  ggplot2::ggtitle("Position 3")

# position 4 ------------------------------------------------------------------

# notes
string_p4 <- c(6, 6,  6, 5, 5,  5, 4, 4,  4, 3, 3,  3, 2,  2, 1, 1,  1)
fret_p4   <- c(7, 8, 10, 7, 8, 10, 7, 9, 10, 7, 9, 10, 8, 10, 7, 8, 10)

# colors
idx_p4 <- c(rep(2, 4), 1, rep(2, 6), 1, rep(2, 5))
pt_fill_p4 <- c("firebrick1", "black")[idx_p4]

# plot
p4 <- tabr::plot_fretboard(string_p4, fret_p4, "notes",
                     fret_range = c(7, 11), show_tuning = TRUE, 
                     point_fill = pt_fill_p4, asp = 1.25, point_size = 8) +
  ggplot2::ggtitle("Position 4")

# position 5 ------------------------------------------------------------------

# notes
string_p5 <- c(6,   6,  6,  5,  5, 4,  4,  4, 3,  3,  3,  2,  2,  2,  1,  1,  1)
fret_p5   <- c(10, 12, 13, 10, 12, 9, 10, 12, 9, 10, 12, 10, 12, 13, 10, 12, 13)

# colors
idx_p5 <- c(rep(2, 2), 1, rep(2, 6), 1, rep(2, 6), 1)
pt_fill_p5 <- c("firebrick1", "black")[idx_p5]

# plot
p5 <- tabr::plot_fretboard(string_p5, fret_p5, "notes",
                     fret_range = c(9, 14), show_tuning = TRUE, 
                     point_fill = pt_fill_p5, asp = 1.25, point_size = 8) +
  ggplot2::ggtitle("Position 5")


# all positions ---------------------------------------------------------------

pA <- tabr::plot_fretboard(
  c(string_p1, string_p2, string_p3, string_p4, string_p5),
  c(fret_p1, fret_p2, fret_p3, fret_p4, fret_p5),
  "notes", horizontal = TRUE, fret_range = c(0, 14), show_tuning = TRUE,
  asp = 0.25, point_size = 8,
  point_fill = c(pt_fill_p1, pt_fill_p2, pt_fill_p3, pt_fill_p4, pt_fill_p5)
  ) +
  ggplot2::ggtitle("All Positions")

```

```{r, fig.height=2.5}
pA
```

```{r, fig.height=6.5}
p1 + p2 + p3 + p4 + p5 + 
  plot_layout(ncol = 3)
```

## Mixolydian

**Intervals:** P1 M2 M3 P4 P5 M6 m7

```{r}
# position 1 ------------------------------------------------------------------

# notes
string_p1 <- c(6, 6, 5, 5, 5, 4, 4, 4, 3, 3, 3, 2, 2, 2, 1, 1)
fret_p1   <- c(3, 5, 2, 3, 5, 2, 3, 5, 2, 4, 5, 3, 5, 6, 3, 5)

# colors
idx_p1 <- c(1, rep(2, 6), 1, rep(2, 6), 1, 2)
pt_fill_p1 <- c("firebrick1", "black")[idx_p1]

# plot
p1 <- tabr::plot_fretboard(string_p1, fret_p1, "notes",
                     fret_range = c(2, 7), show_tuning = TRUE, 
                     point_fill = pt_fill_p1, asp = 1.25, point_size = 8) +
  ggplot2::ggtitle("Position 1")

# position 2 ------------------------------------------------------------------

# notes
string_p2 <- c(6, 6, 6, 5, 5, 5, 4, 4, 3, 3, 3, 2, 2, 2, 1, 1, 1)
fret_p2   <- c(5, 7, 8, 5, 7, 8, 5, 7, 4, 5, 7, 5, 6, 8, 5, 7, 8)

# colors
idx_p2 <- c(rep(2, 6), 1, rep(2, 6), 1, rep(2, 3))
pt_fill_p2 <- c("firebrick1", "black")[idx_p2]

# plot
p2 <- tabr::plot_fretboard(string_p2, fret_p2, "notes",
                     fret_range = c(4, 9), show_tuning = TRUE, 
                     point_fill = pt_fill_p2, asp = 1.25, point_size = 8) +
  ggplot2::ggtitle("Position 2")

# position 3 ------------------------------------------------------------------

# notes
string_p3 <- c(6, 6,  6, 5, 5,  5, 4, 4,  4, 3, 3,  3, 2,  2, 1, 1,  1)
fret_p3   <- c(7, 8, 10, 7, 8, 10, 7, 9, 10, 7, 9, 10, 8, 10, 7, 8, 10)

# colors
idx_p3 <- c(rep(2, 5), 1, rep(2, 6), 1, rep(2, 4))
pt_fill_p3 <- c("firebrick1", "black")[idx_p3]

# plot
p3 <- tabr::plot_fretboard(string_p3, fret_p3, "notes",
                     fret_range = c(7, 11), show_tuning = TRUE, 
                     point_fill = pt_fill_p3, asp = 1.25, point_size = 8) +
  ggplot2::ggtitle("Position 3")

# position 4 ------------------------------------------------------------------

# notes
string_p4 <- c(6,   6,  6,  5,  5, 4,  4,  4, 3,  3,  3,  2,  2,  2,  1,  1,  1)
fret_p4   <- c(10, 12, 13, 10, 12, 9, 10, 12, 9, 10, 12, 10, 12, 13, 10, 12, 13)

# colors
idx_p4 <- c(rep(2, 3), 1, rep(2, 6), 1, rep(2, 6))
pt_fill_p4 <- c("firebrick1", "black")[idx_p4]

# plot
p4 <- tabr::plot_fretboard(string_p4, fret_p4, "notes",
                     fret_range = c(9, 14), show_tuning = TRUE, 
                     point_fill = pt_fill_p4, asp = 1.25, point_size = 8) +
  ggplot2::ggtitle("Position 4")


# position 5 ------------------------------------------------------------------

# notes
string_p5 <- c(6, 6, 6, 5, 5, 5, 4, 4, 4, 3, 3, 2, 2, 2, 1, 1, 1)
fret_p5   <- c(0, 1, 3, 0, 2, 3, 0, 2, 3, 0, 2, 0, 1, 3, 0, 1, 3)

# colors
idx_p5 <- c(rep(2, 2), 1, rep(2, 6), 1, rep(2, 6), 1)
pt_fill_p5 <- c("firebrick1", "black")[idx_p5]

# plot
p5 <- tabr::plot_fretboard(string_p5, fret_p5, "notes",
                     fret_range = c(0, 4), show_tuning = TRUE, 
                     point_fill = pt_fill_p5, asp = 1.25, point_size = 8) +
  ggplot2::ggtitle("Position 5")

# all positions ---------------------------------------------------------------

pA <- tabr::plot_fretboard(
  c(string_p1, string_p2, string_p3, string_p4, string_p5),
  c(fret_p1, fret_p2, fret_p3, fret_p4, fret_p5),
  "notes", horizontal = TRUE, fret_range = c(0, 14), show_tuning = TRUE,
  asp = 0.25, point_size = 8,
  point_fill = c(pt_fill_p1, pt_fill_p2, pt_fill_p3, pt_fill_p4, pt_fill_p5)
  ) +
  ggplot2::ggtitle("All Positions")

```

```{r, fig.height=2.5}
pA
```

```{r, fig.height=6.5}
p1 + p2 + p3 + p4 + p5 + 
  plot_layout(ncol = 3)
```

## Aeolian

**Intervals:** P1 M2 m3 P4 P5 m6 m7

```{r}
# position 1 ------------------------------------------------------------------

# notes
string_p1 <- c(6, 6, 6, 5, 5, 5, 4, 4, 3, 3, 3, 2, 2, 2, 1, 1, 1)
fret_p1   <- c(5, 7, 8, 5, 7, 8, 5, 7, 4, 5, 7, 5, 6, 8, 5, 7, 8)

# colors
idx_p1 <- c(1, rep(2, 6), 1, rep(2, 6), 1, rep(2, 2))
pt_fill_p1 <- c("firebrick1", "black")[idx_p1]

# plot
p1 <- tabr::plot_fretboard(string_p1, fret_p1, "notes",
                     fret_range = c(4, 9), show_tuning = TRUE, 
                     point_fill = pt_fill_p1, asp = 1.25, point_size = 8) +
  ggplot2::ggtitle("Position 1")

# position 2 ------------------------------------------------------------------

# notes
string_p2 <- c(6, 6,  6, 5, 5,  5, 4, 4,  4, 3, 3,  3, 2,  2, 1, 1,  1)
fret_p2   <- c(7, 8, 10, 7, 8, 10, 7, 9, 10, 7, 9, 10, 8, 10, 7, 8, 10)

# colors
idx_p2 <- c(rep(2, 6), 1, rep(2, 6), 1, rep(2, 3))
pt_fill_p2 <- c("firebrick1", "black")[idx_p2]

# plot
p2 <- tabr::plot_fretboard(string_p2, fret_p2, "notes",
                     fret_range = c(7, 11), show_tuning = TRUE, 
                     point_fill = pt_fill_p2, asp = 1.25, point_size = 8) +
  ggplot2::ggtitle("Position 2")

# position 3 ------------------------------------------------------------------

# notes
string_p3 <- c(6,   6,  6,  5,  5, 4,  4,  4, 3,  3,  3,  2,  2,  2,  1,  1,  1)
fret_p3   <- c(10, 12, 13, 10, 12, 9, 10, 12, 9, 10, 12, 10, 12, 13, 10, 12, 13)

# colors
idx_p3 <- c(rep(2, 4), 1, rep(2, 6), 1, rep(2, 5))
pt_fill_p3 <- c("firebrick1", "black")[idx_p3]

# plot
p3 <- tabr::plot_fretboard(string_p3, fret_p3, "notes",
                     fret_range = c(9, 14), show_tuning = TRUE, 
                     point_fill = pt_fill_p3, asp = 1.25, point_size = 8) +
  ggplot2::ggtitle("Position 3")


# position 4 ------------------------------------------------------------------

# notes
string_p4 <- c(6, 6, 6, 5, 5, 5, 4, 4, 4, 3, 3, 2, 2, 2, 1, 1, 1)
fret_p4   <- c(0, 1, 3, 0, 2, 3, 0, 2, 3, 0, 2, 0, 1, 3, 0, 1, 3)

# colors
idx_p4 <- c(rep(2, 3), 1, rep(2, 6), 1, rep(2, 6))
pt_fill_p4 <- c("firebrick1", "black")[idx_p4]

# plot
p4 <- tabr::plot_fretboard(string_p4, fret_p4, "notes",
                     fret_range = c(0, 4), show_tuning = TRUE, 
                     point_fill = pt_fill_p4, asp = 1.25, point_size = 8) +
  ggplot2::ggtitle("Position 4")

# position 5 ------------------------------------------------------------------

# notes
string_p5 <- c(6, 6, 5, 5, 5, 4, 4, 4, 3, 3, 3, 2, 2, 2, 1, 1)
fret_p5   <- c(3, 5, 2, 3, 5, 2, 3, 5, 2, 4, 5, 3, 5, 6, 3, 5)

# colors
idx_p5 <- c(2, 1, rep(2, 6), 1, rep(2, 6), 1)
pt_fill_p5 <- c("firebrick1", "black")[idx_p5]

# plot
p5 <- tabr::plot_fretboard(string_p5, fret_p5, "notes",
                     fret_range = c(2, 7), show_tuning = TRUE, 
                     point_fill = pt_fill_p5, asp = 1.25, point_size = 8) +
  ggplot2::ggtitle("Position 5")

# all positions ---------------------------------------------------------------

pA <- tabr::plot_fretboard(
  c(string_p1, string_p2, string_p3, string_p4, string_p5),
  c(fret_p1, fret_p2, fret_p3, fret_p4, fret_p5),
  "notes", horizontal = TRUE, fret_range = c(0, 14), show_tuning = TRUE,
  asp = 0.25, point_size = 8,
  point_fill = c(pt_fill_p1, pt_fill_p2, pt_fill_p3, pt_fill_p4, pt_fill_p5)
  ) +
  ggplot2::ggtitle("All Positions")

```

```{r, fig.height=2.5}
pA
```

```{r, fig.height=6.5}
p1 + p2 + p3 + p4 + p5 + 
  plot_layout(ncol = 3)
```

## Locrian

**Intervals:** P1 m2 m3 P4 d5 m6 m7

```{r}
# position 1 ------------------------------------------------------------------

# notes
string_p1 <- c(6, 6,  6, 5, 5,  5, 4, 4,  4, 3, 3,  3, 2,  2, 1, 1,  1)
fret_p1   <- c(7, 8, 10, 7, 8, 10, 7, 9, 10, 7, 9, 10, 8, 10, 7, 8, 10)

# colors
idx_p1 <- c(1, rep(2, 6), 1, rep(2, 6), 1, rep(2, 2))
pt_fill_p1 <- c("firebrick1", "black")[idx_p1]

# plot
p1 <- tabr::plot_fretboard(string_p1, fret_p1, "notes",
                     fret_range = c(7, 11), show_tuning = TRUE, 
                     point_fill = pt_fill_p1, asp = 1.25, point_size = 8) +
  ggplot2::ggtitle("Position 1")

# position 2 ------------------------------------------------------------------

# notes
string_p2 <- c(6,   6,  6,  5,  5, 4,  4,  4, 3,  3,  3,  2,  2,  2,  1,  1,  1)
fret_p2   <- c(10, 12, 13, 10, 12, 9, 10, 12, 9, 10, 12, 10, 12, 13, 10, 12, 13)

# colors
idx_p2 <- c(rep(2, 5), 1, rep(2, 6), 1, rep(2, 4))
pt_fill_p2 <- c("firebrick1", "black")[idx_p2]

# plot
p2 <- tabr::plot_fretboard(string_p2, fret_p2, "notes",
                     fret_range = c(9, 14), show_tuning = TRUE, 
                     point_fill = pt_fill_p2, asp = 1.25, point_size = 8) +
  ggplot2::ggtitle("Position 2")


# position 3 ------------------------------------------------------------------

# notes
string_p3 <- c(6, 6, 6, 5, 5, 5, 4, 4, 4, 3, 3, 2, 2, 2, 1, 1, 1)
fret_p3   <- c(0, 1, 3, 0, 2, 3, 0, 2, 3, 0, 2, 0, 1, 3, 0, 1, 3)

# colors
idx_p3 <- c(rep(2, 4), 1, rep(2, 6), 1, rep(2, 5))
pt_fill_p3 <- c("firebrick1", "black")[idx_p3]

# plot
p3 <- tabr::plot_fretboard(string_p3, fret_p3, "notes",
                     fret_range = c(0, 4), show_tuning = TRUE, 
                     point_fill = pt_fill_p3, asp = 1.25, point_size = 8) +
  ggplot2::ggtitle("Position 3")

# position 4 ------------------------------------------------------------------

# notes
string_p4 <- c(6, 6, 5, 5, 5, 4, 4, 4, 3, 3, 3, 2, 2, 2, 1, 1)
fret_p4   <- c(3, 5, 2, 3, 5, 2, 3, 5, 2, 4, 5, 3, 5, 6, 3, 5)

# colors
idx_p4 <- c(rep(2, 2), 1, rep(2, 6), 1, rep(2, 6))
pt_fill_p4 <- c("firebrick1", "black")[idx_p4]

# plot
p4 <- tabr::plot_fretboard(string_p4, fret_p4, "notes",
                     fret_range = c(2, 7), show_tuning = TRUE, 
                     point_fill = pt_fill_p4, asp = 1.25, point_size = 8) +
  ggplot2::ggtitle("Position 4")

# position 5 ------------------------------------------------------------------

# notes
string_p5 <- c(6, 6, 6, 5, 5, 5, 4, 4, 3, 3, 3, 2, 2, 2, 1, 1, 1)
fret_p5   <- c(5, 7, 8, 5, 7, 8, 5, 7, 4, 5, 7, 5, 6, 8, 5, 7, 8)

# colors
idx_p5 <- c(2, 1, rep(2, 6), 1, rep(2, 6), 1, 2)
pt_fill_p5 <- c("firebrick1", "black")[idx_p5]

# plot
p5 <- tabr::plot_fretboard(string_p5, fret_p5, "notes",
                     fret_range = c(4, 9), show_tuning = TRUE, 
                     point_fill = pt_fill_p5, asp = 1.25, point_size = 8) +
  ggplot2::ggtitle("Position 5")

# all positions ---------------------------------------------------------------

pA <- tabr::plot_fretboard(
  c(string_p1, string_p2, string_p3, string_p4, string_p5),
  c(fret_p1, fret_p2, fret_p3, fret_p4, fret_p5),
  "notes", horizontal = TRUE, fret_range = c(0, 14), show_tuning = TRUE,
  asp = 0.25, point_size = 8,
  point_fill = c(pt_fill_p1, pt_fill_p2, pt_fill_p3, pt_fill_p4, pt_fill_p5)
  ) +
  ggplot2::ggtitle("All Positions")

```

```{r, fig.height=2.5}
pA
```

```{r, fig.height=6.5}
p1 + p2 + p3 + p4 + p5 + 
  plot_layout(ncol = 3)
```